\documentclass{scrartcl}
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
\usepackage[nochapters]{classicthesis}
\usepackage[NoDate]{currvita}
\usepackage{url}
\renewcommand{\cvheadingfont}{\LARGE\color{Gray}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
\usepackage{hyperref}		
\hypersetup{	colorlinks,breaklinks,
		urlcolor=Gray, 
		linkcolor=Gray}
\usepackage{eurosym}
\usepackage{color,soul}

\setul{0.3ex}{0.1ex}
\setulcolor{Black}

\newlength{\datebox}\settowidth{\datebox}{August 2006 - Present}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em}
  #2 #3%
\vspace{0.5em}}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}
\newcommand{\Sep}{\vspace{2em}}

\addtolength{\oddsidemargin}{-.35in}
\addtolength{\evensidemargin}{-.35in}
\addtolength{\textwidth}{1in}

\begin{document}
\thispagestyle{empty}

\begin{cv}{
\href{http://www.develmj.com}{\spacedallcaps{Mrityunjay Ravi Iyer}}
}
\Description{\color{Gray}{\scriptsize C1008, Brigade Gardenia,
    J.P. Nagar 7th Phase, Bangalore-560078 }}
\Description{\color{Gray}{\scriptsize email: develmj@gmail.com $\circ$
    mobile: }}

\vspace{1em}


\noindent\spacedlowsmallcaps{\ul{Objective}}
\vspace{0.5em}

\Description{To work in a challenging and innovative environment that
  will allow me to learn and grow as a software engineer and manager}
\vspace{1.5em}

\noindent\spacedlowsmallcaps{\ul{Management Experience}}
\vspace{0.5em}

\NewWorkExperience{\small{October 2011 - May 2012}}{\small{SciSquare TechnoSolutions}}{}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$] Was in charge of hiring and training
  \item[\footnotesize$\bullet$] Built and led the technical and
    development team from scratch
  \item[\footnotesize$\bullet$] Managed customer engagements and new
    business opportunities\MarginDate{CTO and Project Manager}
  \item[\footnotesize$\bullet$] Evangelized Android Mobility to
    companies in the non-mobility consumer space
  \item[\footnotesize$\bullet$] Took charge of project management and product
    management
  \item[\footnotesize$\bullet$] Trained team leads and team members in
    Agile development methodologies and SCRUM
  \item[\footnotesize$\bullet$] Was responsible for product ideation and
    market expansion
  \item[\footnotesize$\bullet$] Handled interaction with corporate
    entities for corporate technical training in Android
\end{itemize}
}

\vspace{0.5em}

\NewWorkExperience{\small{Oct 2008 - July 2011}}{\small{Atlantis
    Computing}}{}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$] Experienced in project management,
    project/issue tracking and people management.
  \item[\footnotesize$\bullet$] In charge of all research and\MarginDate{Engineering Project Manager}
    development projects conducted in the Bangalore centre.
  \item[\footnotesize$\bullet$] Handled delegation and management of
    development support for customer issues.
  \item[\footnotesize$\bullet$] Managed development support for Sales
    Engineering team.
  \item[\footnotesize$\bullet$] Experienced in managing projects with both local and remote team members.
  \item[\footnotesize$\bullet$] Managed multiple projects running simultaneously.
  \item[\footnotesize$\bullet$] Trained and mentored team members in
    Agile software development.
  \item[\footnotesize$\bullet$] Handled technical recruitment and induction.
  \item[\footnotesize$\bullet$] Was the main liaison between US and India teams for projects planning and delegation.

\end{itemize}
}

\vspace{1em}

\noindent\spacedlowsmallcaps{\ul{Technical Experience}}
\vspace{0.5em}

\NewWorkExperience{\small{Aug 2006 - July 2011}}{\small{Atlantis
    Computing}}{}

\vspace{0.5em}

\Description{
\begin{itemize}
\item[\footnotesize$\bullet$] \textbf{Installer: }
  \MarginDate{Atlantis Ilio}{\scriptsize Atlantis Ilio is a storage virtualization solution which provides a
  10X performance increase in VDI storage. Ilio also uses inline Deduplication
  to reduce VDI storage usage by 4X and give up to 95\% IOPS offload. The
  Installer is used to deploy and configure the Ilio virtual appliance for
  customer specific needs.}\\
\vspace{0.5em}
  Role and responsibility: {\scriptsize Conducted the requirement analysis and
  designed the database schema. Designed and developed the command
  line installer. Designed and integrated the email feature into the
  installer. Designed and wrote the custom email module for Ruby.}\\
\vspace{0.5em}
Technologies used: {\scriptsize Ruby, SMTP, Linux dialog, Python, Sqlite, Ubuntu Linux}
\item[\footnotesize$\bullet$] \textbf{Monitoring: }{\scriptsize The Ilio monitoring module is a notification system to inform
administrators regarding server failure, failover or failback (in a high
availability environment) using the integrated email system.}\\
\vspace{0.5em}
Role and responsibility:{\scriptsize Conducted the requirement
  analysis. Designed and developed the email module. Designed and
  integrated modules with the monitoring daemons. Developed the Ruby
  Erlang module.}\\
\vspace{0.5em}
  Technologies used: {\scriptsize Ruby, Erlang, Erlectricity, SMTP, Linux dialog, Ubuntu
  Linux, Bash scripting}
\item[\footnotesize$\bullet$] \textbf{Configurator: }{\scriptsize The Ilio Configurator is an installer/configuration generator.
    The configurator managed networking, installation details and deployment
    details needed to install/deploy the product.}\\
    Role and responsibility:{\scriptsize Was in charge of requirement
      gathering, analysis and database design. Designed and developed
      the configurator UI and the input error processing
      engine. Integrated the Ilio configurator with ISO generation
      tools. Headed the customization of the UI toolkit for single point branding changes.}\\
    \vspace{0.5em}
    Technologies used: {\scriptsize Ruby, Shoes}
\end{itemize}
}

\vspace{0.5em}

\Description{
\begin{itemize}
\item[\footnotesize$\bullet$] \textbf{Active
  Directory:}\MarginDate{Atlantis Unity}{\scriptsize The Active Directory integration with Atlantis
  Unity allowed users to access their Unity account using their enterprise Active
  Directory credentials. This also allowed administrators to control user access,
  permissions and secure login through a single point.}\\
  \vspace{0.5em}
  Role and responsibility:{\scriptsize Was in charge of requirement
    analysis and database schema design. Designed and developed the
    custom Ruby module for Active Directory integration. Developed the
    module to integrate Linux LDAP and Active Directory and developed
    a custom LDAP tree search. Designed and developed a single sign-on
    system for Unity. Also developed a mapping between Active
    Directory and Unity subscriptions.}\\
  \vspace{0.5em}
  Technologies used: {\scriptsize Ruby, Ruby on Rails, LDAP, Active Directory, Awk,
    Gentoo Linux, Nginx}
\item[\footnotesize$\bullet$] \textbf{Netboot V1.0:}{\scriptsize
  Atlantis Netboot v1.0 is a PXE-boot Knoppix based JeOS. The
  JeOS allowed diskless clients to boot into a custom environment and
  seamlessly start up a Windows based virtual machine image using Qemu
  built into the JeOS.}\\
  \vspace{0.5em}
  Role and responsibility: {\scriptsize Performed requirement gathering
  and analysis. Designed and developed a Knoppix Linux based
  JEOS. Designed and re-mastered Knoppix Linux to suite the product
  needs. Integrated Qemu virtualization with the diskless
  JeOS. Integrated the JeOS with the existing Unity
  infrastructure. Customized the JeOS to work with non-standard client
  devices. Designed and developed a secure login into the Netboot JeOS
  integrated to use Unity credentials.}\\
\vspace{0.5em}
Technologies used: {\scriptsize Python, GTK, Linux DHCP server, Knoppix Linux, Qemu,
  Bash scripting}
\item[\footnotesize$\bullet$] \textbf{Netboot V2.0:}{\scriptsize Atlantis Netboot v2.0 involved an enhanced JeOS. This JeOS
used Ubuntu as a base. The user could select a Windows based virtual
machine image and boot into it seamlessly using VMware Player built into the
JeOS. The project also involved working with the Etherboot gPXE team to
integrate gPXE with the Atlantis Netboot solution.
\\(\url{http://etherboot.org/wiki/appnotes/authmenus})}\\
  \vspace{0.5em}
  Role and responsibility: {\scriptsize Performed requirement gathering
  and analysis. Designed and developed an Ubuntu Linux based
  JeOS with an nfs-kernel diskless system. Also integrated Etherboot
  gPXE with Atlantis Netboot. Integrated user Virtual Machine selection with Etherboot
  gPXE during boot process. Created a Customized the linux DHCP server
  to support Netboot. Integrated VMware Player into a diskless Ubuntu
  environment. Designed and developed a secure login system integrated
  with Unity and Active Directory. Designed and developed a Diskless
  Client Control module which allowed remote monitoring and
  shutdown. Developed a MAC address based subscription filter.}\\
\vspace{0.5em}
  Technologies used: {\scriptsize Ruby, GTK, Python, Ubuntu Linux, Linux TPTP server,
  Linux DHCP server, VMware Player, Etherboot gPXE, Active Directory, LDAP,
  NFS, Bash scripting}
\end{itemize}
}

\vspace{0.5em}

\Description{
\begin{itemize}
\item[\footnotesize$\bullet$] \textbf{User signup system: }{\scriptsize Webtop was a web-based service which \MarginDate{Atlantis Webtop}allowed users to
    subscribe to desktop applications hosted on the cloud and access them using
    them remotely using a web-browser. This project allowed users to signup,
    create default user data and subscriptions and send an email on account
    creation.}\\
  \vspace{0.5em}
    Role and responsibility: {\scriptsize Gathered requirements and
      designed the database schema. Designed and developed the
      web-based system. Developed an automated mailer system for
      signed-up users. Developed an automatic backup system for the
      database.}\\
\vspace{0.5em}
    Technologies used: {\scriptsize Ruby, RoR, Action Mailer (RoR), Postgres, Slony,
Gentoo Linux}
  \item[\footnotesize$\bullet$] \textbf{User management system:
  }{\scriptsize The Webtop User management system allowed
administrators to handle all aspects of the user account. It let administrators
set user quotas, modify access rights and application
subscriptions.}\\
    \vspace{0.5em}
    Role and responsibility: {\scriptsize Performed requirement gathering
      and analysis. Designed the complete database schema. Designed and
      developed the web-based administration console. Designed and
      developed the server-side components to perform Linux user
      administration (creation, permissions etc.) Designed and developed
      the quota and subscription management engine.}\\
    \vspace{0.5em}
    Technologies used: {\scriptsize Ruby, Ruby on Rails, Postgres, Gentoo Linux}
  \item[\footnotesize$\bullet$] \textbf{User chat integration:
  }{\scriptsize The Webtop User chat allowed users to chat among
    themselves using an integrated chat client (browser-based).}\\
\vspace{0.5em}
    Role and responsibility: {\scriptsize Designed and developed the
      browser based chat system. Integrated JWChat with the existing
      Ruby on Rails based framework. Configured and integrated
      ejbbaerd with the Rails backend. Designed and developed the user
      chat access rights engine.}\\
    \vspace{0.5em}
    Technologies used: {\scriptsize Ruby, Ruby on Rails, ejabberd, JWChat, XML}
  \item[\footnotesize$\bullet$] \textbf{User monitoring: }{\scriptsize The user monitoring module was used to determine
    Webtop usage statistics. The project involved monitoring subscription usage,
    geographical access, report and trend generation.}\\

\vspace{0.5em}
    Role and responsibility: {\scriptsize Performed requirement
      analysis and database schema design. Designed and developed the
      user logging subsystem. Developed the user access to geolocation
      mapping engine. Designed and developed the trend determination
      engine. Developed the tools for report generation.}\\

\vspace{0.5em}
    Technologies used: {\scriptsize Ruby, Ruby on Rails, Awk, Postgres, Gentoo Linux}
  \item[\footnotesize$\bullet$] \textbf{Google gadget: }{\scriptsize The Webtop Google gadget was a full-featured Webtop
    access console re-written and miniaturized to work within a google gadget.
    This allowed users to integrate their Webtop account into their Google home
    page.}\\
    Role and responsibility: {\scriptsize Gathered and analyzed
      requirements. Designed and developed a miniaturized Webtop
      UI. Designed and developed the Webtop Google Gadget. Developmed
      the Rails backend to support the Google Gadget. Integrated
      Webtop Application Streaming with Google Gadget. Developed a
      secure login system through Google Gadget.}\\
    \vspace{0.5em}
    Technologies used: {\scriptsize Ruby, Ruby on Rails, XML, NX, Gentoo Linux,
    Nginx}
\end{itemize}
}

\vspace{1em}

\noindent\spacedlowsmallcaps{\ul{Technical Skills}}
\vspace{0.5em}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$]Ruby, Python\MarginDate{Programming
    Languages}, C, C++, 
  \item[\footnotesize$\bullet$]Learning Clojure and Erlang
\end{itemize}
}

\vspace{0.5em}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$] \textsl{Operating systems:} GNU/Linux (use and development),
    Windows (use)\MarginDate{Development}
  \item[\footnotesize$\bullet$] \textsl{Frameworks:} Rails (Ruby on Rails)
  \item[\footnotesize$\bullet$] \textsl{Virtualization:} VMWare
    Player, VMWare Workstation, VMWare ESX, VMWare ESXi, VMWare View, Qemu
  \item[\footnotesize$\bullet$] \textsl{Server technologies:} Familiar with High Availability
    systems and storage systems such as NFS, CIFS, NAS, SAN and iSCSI 
  \item[\footnotesize$\bullet$] Working knowledge of Unix System Programming
  \item[\footnotesize$\bullet$] Good knowledge of Shoes (Ruby based GUI toolkit) and working
    knowledge of Gtk (Rubygtk)
  \item[\footnotesize$\bullet$] Experience in full software lifecycle (ideation and design,
 development, testing, packaging and deployment)
  \item[\footnotesize$\bullet$] Good knowledge of Linux OS customization and packaging
  \item[\footnotesize$\bullet$] Good at rapid prototyping of ideas
  \item[\footnotesize$\bullet$] Experienced in Customer support and
    interaction
\end{itemize}
}

\vspace{0.5em}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$] \textsl{Version control tools:} Git, Subversion\MarginDate{Tools}
  \item[\footnotesize$\bullet$] \textsl{Project management tools:} Jira, Green-hopper, Bugzilla, Trac,
    Pivotal Tracker
  \item[\footnotesize$\bullet$] \textsl{Development tools:} Firebug
\end{itemize}
}

\vspace{1em}

\noindent\spacedlowsmallcaps{\ul{Academic Qualifications}}
\vspace{0.5em}

\Description{Dayananda Sagar College of Engineering\MarginDate{B.E. Computer Science}\\Bangalore,
  Karnataka (VTU)\hfill{2006}
}

\vspace{0.7em}

\Description{National Public School (CBSE)\MarginDate{Standard 12}\\Bangalore, Karnataka\hfill{2002}
}

\vspace{0.7em}

\Description{National Public School (CBSE)\MarginDate{Standard 10}\\Bangalore, Karnataka\hfill{2000}
}

\vspace{1em}

\noindent\spacedlowsmallcaps{\ul{Achievements}}
\vspace{0.5em}

\Description{
\begin{itemize}
  \item[\footnotesize$\bullet$] Was part of the team that wrote the
    syllabus and manual (now part of
  standard VTU syllabus) for the seventh
  semester laboratory as well as complete solutions and open-source
  simulator.
  \item[\footnotesize$\bullet$] Organized and co-ordinated the team
    that conducted a simulated HR placement for the third year students of the
    Computer Science department, involving complete mock company presentation to H.R. etc.
  \item[\footnotesize$\bullet$] Was part of the team that organized
    the Entrepreneurship Development program for the final year
    students of our college in the year 2004.
\end{itemize}
}

\end{cv}
\end{document}
